---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  message = FALSE,
  warning = FALSE,
  dev = "ragg_png",
  tidy = "styler",
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CatastRo

<!-- badges: start -->

[![rOS-badge](https://ropenspain.github.io/rostemplate/reference/figures/ropenspain-badge.svg)](https://ropenspain.es/)
[![CRAN-status](https://www.r-pkg.org/badges/version/CatastRo)](https://CRAN.R-project.org/package=CatastRo)
[![CRAN-results](https://cranchecks.info/badges/worst/CatastRo)](https://cran.r-project.org/web/checks/check_results_CatastRo.html)
[![Downloads](https://cranlogs.r-pkg.org/badges/CatastRo)](https://CRAN.R-project.org/package=CatastRo)
[![r-universe](https://ropenspain.r-universe.dev/badges/CatastRo)](https://ropenspain.r-universe.dev/)
[![R-CMD-check](https://github.com/rOpenSpain/CatastRo/workflows/R-CMD-check/badge.svg)](https://github.com/rOpenSpain/CatastRo/actions?query=workflow%3AR-CMD-check)
[![codecov](https://codecov.io/gh/rOpenSpain/CatastRo/branch/master/graph/badge.svg?token=6L01BKLL85)](https://app.codecov.io/gh/rOpenSpain/CatastRo)
[![DOI](https://img.shields.io/badge/DOI-10.5281/zenodo.6044091-blue)](https://doi.org/10.5281/zenodo.6044091)

<!-- badges: end -->

R package to query [Sede Electrónica del
Catastro](http://ovc.catastro.meh.es/ovcservweb/OVCSWLocalizacionRC/OVCCoordenadas.asmx)
API. The API is documented
[here](https://www.catastro.meh.es/ayuda/lang/castellano/servicios_web.htm).

## Installation

```{r eval=FALSE}
library(devtools)
install_github("rOpenSpain/CatastRo")
```

## Query a coordinate

The function `get_rc()` receives the coordinates (lat,lon) and the spatial
reference used. The return is the cadastral reference of the property in that
spatial point, as well as the direction (town street and number).

```{r, eval=FALSE}
library(CatastRo)

reference <- get_rc(lat, lon, SRS)
print(reference)
```

It can be requested to get all the cadastral references in a square of 50-meters
side centered in the coordinates (lat,lon) throught the function `near_rc()`.

```{r, eval=FALSE}
references <- near_rc(lat, lon, SRS)
print(references)
```

## Query CPMRC

It is possible, as well, the opposite. Given to the function `get_coor()` a
cadastral reference, `get_coor()` returns its coordinates (lat,lon) in a
particular SRS moreover the direction (town, street and number).

```{r, eval=FALSE}
direction <- get_coor(Cadastral_Reference, SRS, Province, Municipality)

# The argument SRS could be missed, in that case, `get_coor()` returns the coordinates in the SRS used by Google Maps.

print(direction)
```
