---
title: "CatastRo Package"
author: "Angel Delgado"
date: "`r Sys.Date()`"
output: html_document
vignette: >
  %\VignetteIndexEntry{CatastRo Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Introduction to the API

This R package is aimed to query  the information from the [Sede electrónica del Catastro](http://ovc.catastro.meh.es/ovcservweb/OVCSWLocalizacionRC/OVCCoordenadas.asmx) API directly through a R ide. 

This API is used to retrieve the spatial coordinates of a urban property, moreover it is not needed to be the owner to get the information, actually it is enough to know the casdrastral reference (RC) of the property and its address (in fact, it is only completely compulsory to know the RC, however, to ensure a good result from the response and to avoid mistakes in the RC, the address can be passed to the query too).

Secondly, the API can be used to obtain a RC of a urban property, for this information, the API asks for the longitude and the latitude. Furthermore, it allows to choose the spacial reference system (SRS) between a list of them to express the coordinates.

Finally, the API tackles the issue of not knowning the exact point which the urban property has been registered. In this case, it will return all the properties located in a square 50-meters-side around the given point.

The documentation of this API can be found [here](http://www.catastro.meh.es/ayuda/lang/castellano/servicios_web.htm).

## Installation

The package has been uploaded to GitHub therefore, it can be installed using the `devtools` library.

```{r, message=FALSE, eval=FALSE}
library(devtools)
install_github("rOpenSpain/CatastRo")
```
```{r, message=FALSE}
library(CatastRo)
```

The CatastRo package depends on [httr](https://github.com/r-lib/httr) and [XLM](https://github.com/omegahat/XML) packages. The first one is used to get access to the API through a GET request and the second for parsing the return of the request to a dataframe structure.

## Functions of the package
### Query a coordinate

The function `get_rc()` receives the coordinates (*lat* and *lon*) and the spatial reference system (SRS) used to express them. The return is a list with the casdastral reference of the property in that spatial point, as well as a string with its address (town street and number).


```{r}
reference <- get_rc(lat = 38.6196566583596, lon =  -3.45624183836806, SRS = 'EPSG:4230')
print(reference)
``` 

The function accept as a SRS argument the values "Google" and "Oficial". The first uses the SRS value used by Google maps ('EPSG:4326') while the latter uses the oficial SRS ('EPSG:4258') in Europe. If no SRS is given, the function by default choose the "Google" SRS.

```{r}
reference <- get_rc(lat =  38.6196566583596, lon =-3.45624183836806)
print(reference)
``` 

It is also possible to get all the cadastral references in a square of 50-meters' side centered in the coordinates *lat* and *lon* throught the function `near_rc()`.

```{r}
references <- near_rc(lat = 40.96002, lon = -5.663408, SRS = 'EPSG:4230')
print(references)
``` 

As well as `get_rc()`, `near_rc()` uses SRS = "Google" as a default value.

### Query CPMRC 

The opposite query is possible aswell. Being given to the function `get_coor()` a cadastral reference (*RC*), the province (*Province*) and the town (*Municipality*), `get_coor` returns its coordinates *lat* and *lon* in a particular *SRS* besides the address (town, street and number).

```{r}
direction <- get_coor(RC = '13077A01800039', 
                      SRS = 'EPSG:4230',
                      Province = 'CIUDAD REAL', 
                      Municipality = 'SANTA CRUZ DE MUDELA')
print(direction)
```

The argument *SRS* could be missed, in that case, `get_coor()` returns the coordinates in the SRS = "Google" value too.

```{r}
direction <- get_coor(RC = '13077A01800039', 
                     Province = 'CIUDAD REAL', 
                     Municipality = 'SANTA CRUZ DE MUDELA')
print(direction)
```

Neither the *Province* nor *Municipality* are required to be passed to the function, unless the argument *Municipality* is not null, in that case the  argument *Province* is needed to be passed. If it is passed a value to the *Province* argument while the *Municipality* argument is null, the function `get_coor()` will throw an error.

```{r error=TRUE}
direction <- get_coor(RC = '13077A01800039',  Municipality = 'SANTA CRUZ DE MUDELA')
direction <- get_coor(RC = '13077A01800039')
print(direction)
```

## Integrated tests

The package has been built with integrated test. which ensures to make it automatically check after every update which is made. The approach of these tests are focus in two differents aims: Firstly, to assert that the package pass the `R CMD build` and the `R CMD check` tests automatically. Secondly, we test that the result of the call to the API it is as we expected, if it were not the case, we would go over the function´s scripts to cast them to the new structure of the response of the API.

This action leans in two technologies contained in the package, but they are not part of it.

### Testthat

Testthat is a R-package made by Hadley which can be found in a public repository on GitHub as well as in CRAN. Testthat works with a hierarchical structure testing the results of the functions from the package. The form of each one of our tests are, for instance:

```{r error=TRUE}
library(testthat)
test_that("giving only the cadastral reference", {
  result <- get_coor('9872023VH5797S')
  expect_that((is.numeric(result$coord) & is.character(result$SRS)), is_true())
})

test_that("given Municipio, Provincia is needed", {
  result <- get_coor(RC = '13077A01800039',SRS = 'EPSG:4230', Municipality = 'SANTA CRUZ DE MUDELA')
  expect_that(result, throws_error())
})
```

Every test check an expected value. The test, are gathered in one script for `get_coor()`, `get_rc()` and `near_rc()` separatly. The execution of all  the tasks is made by `testthat.R` and all is contained in the directory [./tests](https://github.com/rOpenSpain/CatastRo/tree/master/tests).

### TravisCI

Travis-CI is a continuous integration service that builds and tests projects that are hosted on GitHub. Apart from the test about the returns of the calls to the API, that have been mentioned, TravisCI take care to prove that the package pass `R CMD check`, which make a variety of diagnostic checks on directory structure, index and control files.

```
language: R

cache: packages
sudo: false
```
