---
title: "CatastRo Package"
author: "Angel Delgado"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{CatastRo Package}
  %\VignetteEngine{knitr::knitr}
  %\VignetteEncoding{UTF-8}
---


R package to query [Sede electrónica del Catastro](http://ovc.catastro.meh.es/ovcservweb/OVCSWLocalizacionRC/OVCCoordenadas.asmx) API. 
The API is documented [here](http://www.catastro.meh.es/ayuda/lang/castellano/servicios_web.htm).

## Installation

```
library(devtools)
install_github("DelgadoPanadero/CatastRo")
```
```{r, include=FALSE}
library(devtools)
install_github("DelgadoPanadero/CatastRo")
library(CatastRo)
```

## Query a coordinate

The function `getRC` recives the coordinates *lat* and *lon* and the spatial reference used. The return is a list with the casdastral reference of the property in that point, as well as its direction (town street and number).


```{r}
reference <- getRC(lat = -3.45624183836806, lon = 38.6196566583596,SRS = 'EPSG:4230')
print(reference)
``` 

If the *SRS* is not given, the spatial reference by default is EPSG:4230.

```{r}
reference <- getRC(lat = -3.45624183836806, lon = 38.6196566583596)
print(reference)
``` 

It is also possible to get all the cadastral references in a square of 50 meters side centered in the coordinates *lat* and *lon* throught the function `getRC_distance`.

```{r}
references <- getRC_distance(lat = -3.45624183836806, lon = 38.6196566583596, SRS = 'EPSG:4230')
print(references)
``` 

## Query CPMRC 

The opposite query is possible as well. Given to the function `getCOOR` a cadastral reference (*RC*), the province (*Province*) and the  town (*Municipality*), `getCOOR` returns its coordinates *lat* and *lon* in a particular *SRS* besides the direction (town, street and number).

```{r}
direction <- getCOOR(RC = '13077A01800039', SRS = 'EPSG:4230',Province = 'CIUDAD REAL', Municipality = 'SANTA CRUZ DE MUDELA')
print(direction)
```

The argument SRS could be missed, in that case, `getCOOR()` returns the coordinates with which was stored.

```{r}
direction <- getCOOR(RC = '13077A01800039', Province = 'CIUDAD REAL', Municipality = 'SANTA CRUZ DE MUDELA')
print(direction)
```

Neither the *Province* nor *Municipality* are required to be passed to the function, unless *Municipality* are given, in that case the  argument *Province* is needed. The function `getCOOR` will throw an error if this happends.

```{r error=TRUE}
direction <- getCOOR(RC = '13077A01800039',  Municipality = 'SANTA CRUZ DE MUDELA')
direction <- getCOOR(RC = '13077A01800039')
print(direction)
```
